---
title: "deduplication"
author: "LR"
date: "09/03/2022"
output: html_document
---
# PFAS exposure of humans, animals and the environment: a Systematic Meta-review Map and Bibliometric analysis  

*Supplementary Material - deduplication code*

## Porpuse: This .Rmd document provides the code we used for deduplication of articles. The file named "articles.csv" contains the output of the searching process of databases. We merged the articles found searching databases using Rayyan.

Total paper uploaded on Rayyan: 2336
Total potential duplicates detected: 1659 
Time needed to resolve 10 potential duplicates on Rayyan: 4 mins
Time expected to resolve 1659 potential duplicates on Rayyan: 11 hours
Since carrying out deduplication on Rayyan was extremely time consuming, we used the following code.

### Setup and packages loading
```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(synthesisr)
library(tidystringdist)
library(bibliometrix)
```
### Loading file
```{r, include=FALSE}
dat <- read.csv(here("data/deduplication_process/articles.csv"))
dim(dat) #[1] 2446   19
```
### Tidy up and simplify titles removing all punctuation and extra white spaces
```{r, include=FALSE}
dat$title2 <- str_replace_all(dat$title,"[:punct:]","") %>% str_replace_all(.,"[ ]+", " ") %>% tolower()
```
### Remove extra title matches
```{r, include=FALSE}
dat2 <- distinct(dat, title2, .keep_all = TRUE) #select records with unique titles (removes exact duplicates)
dim(dat2) #[1] 1630   20
```
### Removing partial matches in titles
```{r, include=FALSE}
duplicates_string <- find_duplicates(dat2$title2, method = "string_osa", to_lower = TRUE, rm_punctuation = TRUE, threshold = 7)
dat3 <- extract_unique_references(dat2, duplicates_string)
dim(dat3) #[1] 1562   21
```
### Manually review those titles to confirm they are duplicates
```{r, include=FALSE}
manual_checks <- review_duplicates(dat2$title, duplicates_string)
#view(manual_checks)
dat3 <- extract_unique_references(dat2, duplicates_string)
dim(dat3) #[1] 1562   21
```
### Drop columns "title2" and "n_duplicates"
```{r, include=FALSE}
dat4 <- select(dat3, -c(title2,n_duplicates))
dim(dat4) #[1] 1562   19
```
### Save as a .bib file to upload on Zotero. Then export from Zotero as .ris file to reimport into Rayyan
```{r, include=FALSE}
write_refs(dat4, format = "bib", file = here("data/deduplication_process/abstracts_for_screening_deduplicated.bib"))
```

Deduplicated articles uploaded on Rayyan (Review named PFAS_Evidence_Review_Map_deduplicated): 1562
Total potential duplicates detected: 60
We resolved manually these 60 potential duplicates on Rayyan.